Manuscript

### 2022-09-07 analysis/manuscript.Rmd
change label for "C-sum"

  theme_minimal() +
  ggplot2::labs(x = paste0("C sum"),
                y = paste("Correlation - MR-estimate")) +
  theme(legend.title=element_blank()) +
  geom_text_repel(data = subset(max_C_data, label_phenos==TRUE),
                  nudge_y = -0.25 - subset(max_C_data, label_phenos==TRUE)$same_trait_corr_minus_MR_est, size = 3.25,
                  direction = "x", show.legend = FALSE, box.padding = 0.5)

>>>>

  theme_minimal() +
  ggplot2::labs(x = paste0("C-sum"),
                y = paste("Correlation - MR-estimate")) +
  theme(legend.title=element_blank()) +
  geom_text_repel(data = subset(max_C_data, label_phenos==TRUE),
                  nudge_y = -0.25 - subset(max_C_data, label_phenos==TRUE)$same_trait_corr_minus_MR_est, size = 3.25,
                  direction = "x", show.legend = FALSE, box.padding = 0.5)
